Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-09-27 paper.tex
start of modularity + some notes

        \section{Modularity}\label{mod}
        \section{Workflow sharing}\label{sharing}
    \chapter{Performance}\label{performance}
        \section{Filesystems}
        \section{Scheduling}
        \section{Performance enhancement strategies}
    \chapter{Portability}\label{portability}
        \section{Containers}
    \chapter{Reproducibility}\label{reproducibility}
        \section{Provenance Tracking}
        \section{containerization}
    \chapter{Discussion/Conclusion}

>>>>

        \section{Modularity}\label{mod}
            Often times, users will want to integrate existing tools, in 
            addition to custom scripts, into their workflows. As workflow 
            engines, with the exception of Make, are typically not written in 
            Shell, it is necessary to create interfaces to these tools. These
            interfaces may range from simple calls to the command-line, to more 
            complex ones that track inputs, outputs and other parameters; ensure
            that all parameters are specified in the correct order and that the
            parameter and file types are all correct; capture all of the 
            standard input/output; and create folders to encapsulate task inputs
            and outputs. Workflow engines typically rely on more complex types 
            of interfaces in order to ensure correct functioning of the pipeline
            . As these interfaces can be rather complex, it is necessary for the 
            workflow engine to provide an intuitive way for users to create 
            interfaces for their custom tools.

            Early neuroimaging workflow engines, such as SPM, are monolithic, 
            thus preventing users from incorporating their custom workflows

        \section{Workflow sharing}\label{sharing}
    \chapter{Performance}\label{performance}
        \section{Filesystems}
            scientific: shared FS such as Lustre, NFS, S3
            big data: mapreduce - HDFS, spark and dask shared or distributed
        \section{Scheduling}
            scientific: SLURM, PBS, SGE, HTCondor, Mesos (sometimes)
            big data: mapreduce - local or YARN, Spark - standalone, YARN or 
            Mesos, dask: any (easy to extend to any scheduler)
        \section{Performance enhancement strategies}
            scientific: not much
            big data: data locality, in memory computing, lazy evaluation
    \chapter{Portability}\label{portability}
        java or python backend (most) typically platform independent (some 
        exceptions)
        all tools used in the pipeline must be installed on system
        Taverna - exception as relies on web services
        \section{Containers}
            use of containers increase portability. none of the scientific 
            pipelines can be containerized and communicate with the scheduler 
            outside of the container
            big data frameworks can
    \chapter{Reproducibility}\label{reproducibility}
        \section{Provenance Tracking}
        big data frameworks: limited to lineage
        \section{containerization}
    \chapter{Discussion/Conclusion}
